Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-09-13 paper/self_calibration_I.tex
typo

Ultimately, survey design requires trade-offs between calibration
requirements and other requirements related to cadence, telescope
overheads, and observing constraints (like alt, az, airmass, and
field-rotation constraints).  One requirement that is often
over-emphasized, however, is conceptual or apparent ``uniformity'';
these these different survey strategies have different uniformities of
coverage, each with possibly non-obvious consequences.  Many
astronomers will see survey strategy A as being ``more uniform'' in
its coverage (especially relative to survey D).  This is not true, if
uniformity is defined by the variance or skewness or any other simple
statistic in exposure times; strategy D is extremely uniform (more
uniform than Poisson, for example).  In any survey, past and future,
variations in exposure time have been valuable for checking systematic
and random errors, and don't---in themselves---make it difficult to
obtain a uniform survey in properties like brightness (since samples
can be cut on any well-measured property).  In general, in the
presence of real astronomical variations in distributions of
luminosity, distance, metallicity, and (more importantly) extinction
by dust, there is no way to make a survey uniformly sensitive to the
objects of interest.  As a community we should be prepared to adjust
our analysis for the non-uniformity of the survey rather than adjust
(cut) our data to match the uniformity of unrealistically simplified
analyses.  This is already standard practice in the precise
cosmological measurement experiments, and will be required practice
for the next generation of massively-multiple-epoch imaging surveys.

>>>>

Ultimately, survey design requires trade-offs between calibration
requirements and other requirements related to cadence, telescope
overheads, and observing constraints (like alt, az, airmass, and
field-rotation constraints).  One requirement that is often
over-emphasized, however, is conceptual or apparent ``uniformity'';
these different survey strategies have different uniformities of
coverage, each with possibly non-obvious consequences.  Many
astronomers will see survey strategy A as being ``more uniform'' in
its coverage (especially relative to survey D).  This is not true, if
uniformity is defined by the variance or skewness or any other simple
statistic in exposure times; strategy D is extremely uniform (more
uniform than Poisson, for example).  In any survey, past and future,
variations in exposure time have been valuable for checking systematic
and random errors, and don't---in themselves---make it difficult to
obtain a uniform survey in properties like brightness (since samples
can be cut on any well-measured property).  In general, in the
presence of real astronomical variations in distributions of
luminosity, distance, metallicity, and (more importantly) extinction
by dust, there is no way to make a survey uniformly sensitive to the
objects of interest.  As a community we should be prepared to adjust
our analysis for the non-uniformity of the survey rather than adjust
(cut) our data to match the uniformity of unrealistically simplified
analyses.  This is already standard practice in the precise
cosmological measurement experiments, and will be required practice
for the next generation of massively-multiple-epoch imaging surveys.
